---
title: "Coding Assignment 2"
author: "Team 10"
date: "10/23/2022"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
#Put any packages you need here
knitr::opts_chunk$set(echo = TRUE)
```

A Florida health insurance company wants to predict annual claims for individual clients. The company pulls a random sample of 50 customers. The owner wishes to charge an actuarially fair premium to ensure a normal rate of return. The owner collects all of their current customer’s health care expenses from the last year and compares them with what is known about each customer’s plan. 

The data on the 50 customers in the sample is as follows:

-	Charges: Total medical expenses for a particular insurance plan (in dollars)
-	Age: Age of the primary beneficiary
-	BMI: Primary beneficiary’s body mass index (kg/m2)
-	Female: Primary beneficiary’s birth sex (0 = Male, 1 = Female)
-	Children: Number of children covered by health insurance plan (includes other dependents as well)
-	Smoker: Indicator if primary beneficiary is a smoker (0 = non-smoker, 1 = smoker)
-	Cities: Dummy variables for each city with the default being Sanford

Answer the following questions using complete sentences and attach all output, plots, etc. within this report.


```{r dataset, include=FALSE}
insurance <- read.csv("../Data/insurance_0126_Group10.csv")
```



## Question 1

Generate this regression equation:

$$Charges = \beta_{0}+\beta_{1}*Age+\beta_{2}*BMI+\beta_{3}*Children + \beta_{4}*Female + \beta_{5}*Smoker + \beta_{6}*WinterSprings + \beta_{7}*WinterPark + \beta_{8}*Oviedo$$

```{r q1} 
insurancereg <- lm(Charges ~ Age + BMI + Children + Female + Smoker + WinterSprings + WinterPark + Oviedo, data = insurance)

summary(insurance)
```
$$Charges ={-18140.8}+{199.1}*Age+{643.4}*BMI{-187.2}*Children + {1465.5}*Female+{24548.2}*Smoker{-2672.2}*WinterSprings {-5045.6}*WinterPark+{1671.7}*Oviedo$$
Which independent variables test significant in a two-tailed test? Use $\alpha = 0.2$
$P<\alpha$
$$AGE-PValue = {0.004160}<\alpha$$
Age: At α = .02 level, p is less than α, reject null hypothesis, conclude Age has significant effect on charges. 

$$BMI-PValue = {0.00281}<\alpha$$
BMI: At α = .02 level, p is less than α, reject null hypothesis, conclude BMI has significant effect on charges. 

$$Smoker-PValue = {9.35e-13}<\alpha$$
Smoker: At α = .02 level, p is less than α, reject null hypothesis, conclude Smoker has significant effect on charges. 

$$WinterPark-PValue = {0.050341}<\alpha$$
Winter Park: At α = .02 level, p is less than α, reject null hypothesis, conclude Winter Park has significant effect on charges. 

## Question 2

Interpret the coefficients of all the independent variables that tested significant.

$$Charges ={-18140.8}+{199.1}*Age+{643.4}*BMI{-187.2}*Smoker{-2672.2}*WinterPark+{1671.7}$$
Coefficient of Age: 199.1; on average, all else equal, each additional year in Age will increase charges by $199.1.

Coefficient of Winter Park: 1671.7; on average, all else equal, charges are $1671.7 higher for residents of Winter Park than residents of Sanford

BMI and Smoker have a significant inverse effect on charges (decrease charges). 

Coefficient of BMI: -187.2; on average, all else equal, each additional unit of BMI will decrease charges by $187.2.

Coefficient of Smoker: -2672.2; on average, all else equal, charges are $-2672.2 ;lower for smokers than non-smokers

## Question 3

The insurance agent returns with another client:

- Age: 35
- BMI: 26
- Children: 1
- Gender: Female
- Smoker: No
- City: Sanford
$$Charges ={-18140.8}+{199.1}*Age+{643.4}*BMI{-187.2}*Children + {1465.5}*Female+{24548.2}*Smoker{-2672.2}*WinterSprings {-5045.6}*WinterPark+{1671.7}*Oviedo$$

Using the regression equation above, predict the amount of medical expenses associated with this policy. (Provide a 95% confidence interval as well)


``` {r q3}
newPrediction <- data.frame(Age = 35,
                            BMI = 26,
                            Children = 1,
                            Female = 1,
                            Smoker = 0,
                            WinterSprings = 0,
                            WinterPark = 0,
                            Oviedo = 0)

predict(insurancereg, newdata = newPrediction,
        interval = "confidence",
        level = .95)
```
Charges = 6833.54

95% confidence interval: 
{2348.908, 11318.17}

## Question 4

Compare the model from question 1, to a model that does not include the group of city dummies. Does including the cities reduce the SSE by a statistically significant amount? (check the partial F-test for significance of the dummies as a group). Use $\alpha = 0.05$
```{r q4} 
insurancereg2 <- lm(Charges ~ Age + BMI + Children + Female + Smoker, data = insurance)

summary(insurance)
```

```{r q5}
nnewPrediction <- data.frame(Age = 35,
                            BMI = 26,
                            Children = 1,
                            Female = 1,
                            Smoker = 0,
                            WinterSprings = 0,
                            WinterPark = 0,
                            Oviedo = 0)

predict(insurancereg2, newdata = newPrediction,
        interval = "confidence",
        level = .95)
```
```{r q6}

reduced_sat <- insurancereg2

model_reduced <- lm(Charges ~., data =as.data.frame(insurance))

summary(model_reduced)
```
```{r q7}
anova(model_reduced, insurancereg2)
```
F = [(SSEreduced - SSEfull)/m]/SSEfull/n-k-1
F = [(1899859523-1548987760)/3]/1548987760/50-8-1
F = [(350871763/3)]/1548987760/41
F = 116957254.33/37780189.27
F = 3.09
Critical F-Value = Studenmund F tables: F(m, n − k − 1)
F(3,41)
Critical F-Value = 2.84
F > Critical F-Value = 3.09 > 2.84
The partial F-test produced a value greater than the critical F-value, meaning that the group of city dummies will reduce the SSE by a statistically significant amount.


